Pilot study Aperol: questionnaire data

### 2021-01-07 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
questionnaire update

# filter by parameter variable, i.e. create a subset for each group (expert/novice/experimenter)
km.data <- raw.data %>% filter(item == "Klassenmanagement",
                               value.1 != "n.a.")

# print(km.data)

# value sometimes contained text before filtering, we have to convert the numbers to numeric
km.data <- km.data %>%  mutate(value = as.numeric(as.character(factor(value.1))))

# create  mean, min, max, sd of classroom management
meankm <- mean(km.data$value.1)
minModul <- min(Modul.data$value)
maxModul <- max(Modul.data$value)
sdModul <- sd(Modul.data$value)
NModul<-length(unique(Modul.data$ID))
# filter by parametervariable, i.e. create a subset for the individual lecturer
ind.Modul.data <- Modul.data %>% filter(Dozierende == params$Dozierende)
# erstelle Mittelwert, min, max, sd for individual lecturer
ind.meanModul <- mean(ind.Modul.data$value)
ind.minModul <- min(ind.Modul.data$value)
ind.maxModul <- max(ind.Modul.data$value)
ind.sdModul <- sd(ind.Modul.data$value)
ind.NModul<-length(unique(ind.Modul.data$ID))
```

test.ind.data <- raw.data %>%
  filter(what == "data" & valid == "1" & trialtype == "test") %>%
  select(id, age, condition, correct)  %>%
  mutate(correct = as.integer(correct),
         age = as.factor(age),
         condition = as.factor(condition),
         groups = paste(age,"-",condition)) %>%
  group_by(groups, age, condition, id) %>%
  summarise(proportion.correct = round(mean(correct)*100, 2))

test.all.data <- raw.data %>%
  filter(what == "data" & valid == "1" & trialtype == "test") %>%
  select(id, age, condition, correct)  %>%
  mutate(correct = as.integer(correct),
         age = as.factor(age),
         condition = as.factor(condition),
         groups = paste(age,"-",condition)) %>%
  group_by(groups, age, condition) %>%
  summarise(proportion.correct = round(mean(correct)*100, 2),
            sd = round(sd(correct)*100,2))

test.raw.data <- raw.data %>%
  filter(what == "data" & valid == "1" & trialtype == "test") %>%
  select(id, age, condition, correct)  %>%
  mutate(correct = as.integer(correct),
         age = as.factor(age),
         condition = as.factor(condition),
         groups = paste(age,"-",condition))

test.boxplot <-ggplot() +
  geom_boxplot(data = test.ind.data, aes(x = groups, y = proportion.correct), )+ # when there is more data add "notch = TRUE" for conf intervalls
  geom_jitter(data = test.ind.data, aes(x = groups, y = proportion.correct, colour=condition), size = 2, width = 0.1) +
    scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,102))+
  labs(x="Groups", y="Proportion Correct")+ # for title add --> title="Proportion of Correct Choices", 
  theme_classic()
   # geom_violin(data = test.raw.data, trim = TRUE , adjust = .7, draw_quantiles = c(0.5), mapping = aes(x=groups, y = correct))
test.boxplot

### Performance across trials
Children are tested without feedback. The experimenter merely acknowledges the participant's choice by saying "thank you". The plot below presents the proportion of correct choices across all test trials for both age groups and conditions.

```{r plot linegraph performance across trials, echo=FALSE}

>>>>

# filter by parameter variable, i.e. create a subset for each group (expert/novice/experimenter)
km.data <- raw.data %>% filter(item == "Klassenmanagement")

view (raw.data)

# value sometimes contained text before filtering, we have to convert the numbers to numeric
km.data <- km.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# create  mean, min, max, sd of classroom management
meankm <- mean(km.data$value)
minkm <- min(km.data$value)
maxkm <- max(km.data$value)
sdkm <- sd(km.data$value)
Nkm<-length(unique(km.data$ID))

# # filter by parametervariable, i.e. create a subset for the individual lecturer
# ind.km.data <- km.data %>% filter(Dozierende == params$Dozierende)
# # erstelle Mittelwert, min, max, sd for individual lecturer
# ind.meankm <- mean(ind.km.data$value)
# ind.minkm <- min(ind.km.data$value)
# ind.maxkm <- max(ind.km.data$value)
# ind.sdkm <- sd(ind.km.data$value)
# ind.Nkm<-length(unique(ind.km.data$ID))
```
The mean of the item "classroom management" is `r round(meankm, 2)` (min = `r minkm`; max = `r maxkm`; SD = `r round(sdkm,2)`; N = `r Nkm)`; lickert-scale 1-4; 4 = best rating).

```{r classroom management horicontal Plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}
# filter by parametervariable, i.e. create a subset for the individual lecturer
km.data <- raw.data %>% filter(item == "Klassenmanagement")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
km.data <- km.data %>%  mutate(value = as.numeric(as.character(factor(value))))

view(km.data)
# to stick to the individual vs all style necessary for anonymized feedback in plotting
# we create a new vector from experiece that we call "expert" and copy the names
# of the name called by the parameter but rename all others to "all"
# now the "fill ="option can use the new column to differentiate all vs parameter dozent

km.plot.data <- km.data %>%
  mutate(Teilnehmende = ifelse(Dozierende == params$Dozierende, toString(params$Dozierende), "Alle Kurse"))
modul.plot.data$Teilnehmende <- as.factor(modul.plot.data$Teilnehmende)

# to create error bars, we need to summarise the data in a seperate dataframe
modul.plot.sd <-modul.plot.data %>% 
  group_by(itemfulltext, Teilnehmende, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# and here comes the long plot 
modul.plot<-ggplot(data = modul.plot.sd, 
                           aes(x = itemfulltext, y = mean, 
                               group=Teilnehmende, colour = Teilnehmende)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,5)+
  labs(data = modul.plot.data, y = "Ausprägung", x = NULL,
       title="Modulbewertung" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
modul.plot

```
```{r plot linegraph performance across trials, echo=FALSE}
